
\documentclass[a4paper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty (A4-optimized inline)
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% --- Adjust margins for A4 and compact layout ---
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.6in}

\setlength{\multicolsep}{-5pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{6pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{1pt}
    \footnotesize{#2}
    \vspace{1pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10pt}
  \fancyfoot[C]{\footnotesize #1}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

\newcommand{\headingBf}[2]{\heading{\textbf{#1}}{\textbf{#2}}}
\newcommand{\headingIt}[2]{\heading{\textit{#1}}{\textit{#2}}}

\newenvironment{resume_list}{
  \vspace{-6pt}
  \begin{itemize}[itemsep=-1px, parsep=0pt, leftmargin=28pt]
}{
  \end{itemize}
}

\renewcommand\labelitemi{--}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%======================%
% Header + Summary     %
%======================%

\documentTitle{
  {\Huge\textbf{Ata Safapour}}\\[3pt]
  {\Large\color{accentText}\textbf{Software Engineer}}
  }{
    \href{tel:+989146982635}{\raisebox{-0.05\height}\faPhone\ +98 914 698 2635} ~ | ~
    \href{mailto:safapour.ata@gmail.com}{\raisebox{-0.15\height}\faEnvelope\ safapour.ata@gmail.com} ~ | ~
    \href{https://linkedin.com/in/ata-safapour}{\raisebox{-0.15\height}\faLinkedin\ ata-safapour} ~ | ~
    \href{https://github.com/ata-the-legend}{\raisebox{-0.15\height}\faGithub\ ata-the-legend}
    }
    
    
    %---------%
    % Summary %
    %---------%
    \tinysection{Summary}
    Software Engineer with 2+ years of experience architecting scalable microservices and event-driven systems using Python and FastAPI. Passionate about solving complex technical challenges and delivering high-quality software solutions.
    
    
    %--------%
    % Skills %
    %--------%
    \section{Skills}
    \begin{multicols}{2}
      \begin{itemize}[itemsep=-2px, parsep=0pt, leftmargin=70pt]
        \item[\textbf{Languages}] Python
        \item[\textbf{Frameworks}] FastAPI, Django, Flask, Celery, FastStream
        \item[\textbf{Databases}] MongoDB, PostgreSQL, MySQL
        \item[\textbf{DevOps}] Docker, Git, GitLab CI/CD, Proxmox, Tailscale
        \item[\textbf{Monitoring}] Sentry, Prometheus, Grafana, ELK Stack
        \item[\textbf{Other Tools}] Ansible, Casdoor, Pi-hole, Mailu, Jitsi, RabbitMQ, Kong
      \end{itemize}
    \end{multicols}
    
    %-----------%
    % Education %
    %-----------%
    \section{Education}
    
    \headingBf{University of Tehran}{2021 -- 2024}
    \headingIt{Master’s in Power Electronics}{}
    \begin{resume_list}
      \item Ranked \textbf{4th} in the National Master’s Entrance Exam (Power Electronics).
      \item Designed control algorithms for grid-connected inverters to minimize DC-link oscillations.
    \end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Torfehnegar Holding}{May 2024 -- Present}
\headingIt{Software Engineer}{Tehran, Iran}
\begin{resume_list}
  \item Architected and developed \textbf{event-driven microservices platform} using \textbf{FastAPI} and \textbf{RabbitMQ}, enabling asynchronous communication between services through signal-based messaging patterns.
  \item Led \textbf{monolithic-to-microservices migration} using \textbf{strangler-fig pattern}, successfully decomposing legacy system while maintaining zero downtime and backward compatibility.
  \item Engineered \textbf{multi-tenant SaaS platform} with tenant isolation at database and application layers, supporting scalable B2B operations across multiple organizations.
  \item Designed and implemented \textbf{Meet Microservice} integrating multiple third-party providers (Jitsi, etc.) with \textbf{Factory design pattern} for provider abstraction and permission management.
  \item Built \textbf{Direct Meet Scheduling Service} orchestrating interactions between Persona, Meet, and Notification microservices for seamless individual appointment booking.
  \item Developed \textbf{Course Management Microservice} supporting online, offline, and in-person formats using \textbf{OOP generic classes}, integrating with Notify, Meet, Space, File, and Persona services.
  \item Maintained and enhanced \textbf{IAM microservice} based on \textbf{Casdoor} with \textbf{sidecar pattern}, managing role assignments and SSO whitelist functionality for secure authentication.
  \item Migrated database layer from \textbf{Motor async driver} to \textbf{Beanie ODM}, improving code maintainability and developer productivity with schema validation and type safety.
  \item Implemented \textbf{Kong API Gateway} for centralized routing, rate limiting, and authentication across microservices ecosystem.
  \item Optimized \textbf{MongoDB} query performance by \textbf{40\%} through indexing strategies and aggregation pipeline optimization, significantly reducing API response times.
  \item Built secure \textbf{multi-data-center network} using \textbf{Tailscale} mesh VPN and \textbf{Pi-hole} for DNS-level security and network segmentation.
  \item Established \textbf{CI/CD pipelines} with \textbf{GitLab Actions} for automated testing, building, and deployment across staging and production environments.
  \item Deployed comprehensive \textbf{observability stack} (\textbf{Sentry}, \textbf{Prometheus}, \textbf{Grafana}) for real-time monitoring, error tracking, and performance metrics visualization.
  \item Managed isolated development and staging environments on \textbf{Proxmox VE}, enabling parallel feature development and thorough testing before production releases.
  \item Deployed and maintained internal self-hosted services (\textbf{Mailu} email, \textbf{Jitsi} video conferencing) to reduce external dependencies and operational costs.
\end{resume_list}

\headingBf{Freelance}{Mar 2023 -- May 2024}
\headingIt{Backend Developer}{Remote}
\begin{resume_list}
  \item \textbf{E-commerce Platform:} Full-stack Django/DRF system with Celery \& RabbitMQ; secure payment and async processing.
  \item \textbf{LLM-Powered Semantic Search:} Retrieval-Augmented Generation (RAG) system for semantic query handling using LLMs.
  \item \textbf{ASR \& Translation Tool:} Real-time English ASR integrated with multilingual translation APIs.
\end{resume_list}


%-----------------%
% Certifications %
%-----------------%
\section{Certifications}

\headingBf{Daneshkargroup}{2023}
\headingIt{Python / Django Coding Bootcamp}{}
\begin{resume_list}
  \item Completed intensive backend training focused on Python, Django, and RESTful API development.
\end{resume_list}
%-----------%
% Projects %
%-----------%
% \section{Projects}

% \headingBf{LLM-Based Semantic Search System}{2024}
% \begin{resume_list}
%   \item Developed a retrieval system integrating transformer models and vector databases for semantic search.
% \end{resume_list}

% \headingBf{Automated CI/CD Stack}{2024}
% \begin{resume_list}
%   \item Built a self-hosted deployment and monitoring stack using GitLab, Docker, Prometheus, and Grafana.
% \end{resume_list}

\documentFooter{\thepage/\pageref{LastPage}}

\end{document}

% great. lets dive in to experiance section
% this so general
% Architected a multi-tenant microservices platform with FastAPI.

% lets break it to some better bullet points
% i will decribe my work and you should suggest some bullet points for them. bold importent key words on each bullet point. give me some advice to make this perfect.

